Open-Set Domain Adaptation through Self-Supervision

### 2022-02-12 paper/main.tex
Step II updated

In this step,
having separated the target into a known part $\mathcal{D}_t^{knw}$,
and an unknown part $\mathcal{D}_t^{unk}$,
we arrange two new datasets in order to perform the domain alignment while also learning
the unknown class.
The first one is $\mathcal{D}_s^*$, composed as $\mathcal{D}_s \cup \mathcal{D}_t^{unk}$,
which contains the original source images plus the target images identified as unknown classes.
We thus set the labels for $\mathcal{D}_t^{unk}$ as the class {\it unknown}.
The second one is $\mathcal{D}_t^{knw}$, which can be used to perform the domain alignment
without the risk of negative transfer.
While the feature extractor $E$ is inherited from the previous stage and leverages the previous training phase,
we also use two new classifiers,
$C_2$ and $R_2$.
They are similar to the previous classifiers but they have two important differences.
$C_2$ now has a $(|\mathcal{C}_s|+1)$-dimensional output to accomodate also the unknown class predictions and also
benefits from the previous learning,
while $R_2$ is always a single-head rotation classifier and starts the learning from scratch.
The training phase is the same as before with the difference that we do not have the center loss this time.
We also employ a different hyperparameter $\alpha_2$ to weigh the rotation classifier loss contribution.
The objective function is again $\mathcal{L}_2 = \mathcal{L}_{C_2} + \mathcal{L}_{R_2}$,
where the two contributions are identical to equations \ref{eq:baseloss_class} and \ref{eq:baseloss_rot}.
We report the $\mathcal{L}_{R_2}$ loss contributions to make clear the usage of $\alpha_2$ and we
recall that $\mathcal{L}_{C_2}$ is now computed using the new arranged dataset $\mathcal{D}_s^*$.

>>>>

In this step,
having separated the target into a known part $\mathcal{D}_t^{knw}$,
and an unknown part $\mathcal{D}_t^{unk}$,
we arrange two new datasets in order to perform the domain alignment while also learning
the unknown class.
The first one is $\mathcal{D}_s^*$, composed as $\mathcal{D}_s \cup \mathcal{D}_t^{unk}$,
which contains the original source images plus the target images identified as unknown classes.
We thus set the labels for $\mathcal{D}_t^{unk}$ as the class {\it unknown}.
The second one is $\mathcal{D}_t^{knw}$, which can be used to perform the domain alignment
without the risk of negative transfer.
While the feature extractor $E$ is inherited from the previous stage and leverages the previous training phase,
we also use two new classifiers,
$C_2$ and $R_2$.
They are similar to the previous classifiers but they have two important differences.
$C_2$ now has a $(|\mathcal{C}_s|+1)$-dimensional output to accomodate also the unknown class predictions and also
benefits from the previous learning,
while $R_2$ is always a single-head rotation classifier and starts the learning from scratch.
The training phase is the same as before with the difference that we do not have the center loss this time.
We also employ a different hyperparameter $\alpha_2$ to weigh the rotation classifier loss contribution.
The objective function is again $\mathcal{L}_2 = \mathcal{L}_{C_2} + \mathcal{L}_{R_2}$,
where the two contributions are identical to equations \ref{eq:baseloss_class} and \ref{eq:baseloss_rot}.
We report the $\mathcal{L}_{R_2}$ loss contribution to make clear the usage of $\alpha_2$ and we
recall that $\mathcal{L}_{C_2}$ is now computed using the new arranged dataset $\mathcal{D}_s^*$.
